Regression

### 2018-02-08 paper/R/02_cleanAndCombine.Rmd
more filtering

  # remove articles about the weater
  filter(!grepl("wetter", url)) %>%
  filter(!grepl("Deutsche Bahn", text) | site!="Tagesschau.de")
```

@@

## Preparation
```{r}
btw <- btw %>% 
  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
  filter(!grepl("Deutsche Bahn", text) | site!="Tagesschau.de")
```

>>>>

  # remove articles about the weater
  filter(!grepl("wetter", url)) %>%
  filter(!grepl("sturm", url) |
           site != "Tagesschau.de") %>%
  filter(!grepl("Deutsche Bahn", text) | 
           site!="Tagesschau.de") %>%
  filter(!grepl("bahnstrecke", text) | 
           site!="Tagesschau.de")
```

@@

## Preparation
```{r}
btw <- btw %>% 
  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private"))
  filter(!grepl("sturm", url) |
           site != "Tagesschau.de") %>%
  filter(!grepl("Deutsche Bahn", text) | 
           site!="Tagesschau.de") %>%
  filter(!grepl("bahnstrecke", text) | 
           site!="Tagesschau.de")
```

### 2018-02-08 paper/R/04_Modelresults.Rmd
more filtering

# 2. Data 
```{r caching, echo = FALSE}
#load("../output/btw_combined.Rda")
load("../output/btw_comb_ownership.Rda")
```

@@

# 3. Model Results
```{r caching, echo = FALSE}
#load("../output/models/STM_stemmed2 40 .Rda")
load("../output/models/STM_ownership 40 .Rda")
out <- out_ownership
```

@@

After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
```{r}
sagelabs$cov.betas[[2]]$problabels[,1:6]
```

```{r}
topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition",
                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder",
                   7, "political trends after the election", 8, "Merkel vs.Schulz", 9, "Trends in electoral districts", 
                   10, "Steinmeier, Federal President", 11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
                   12, "Federal Election trends", 13, "Climate policy", 14, "G20 Hamburg", 
                   15, "error (text processing failure)", 16, "Federal budget statistics", 
                   17, "Reports on individuals (Berlin)", 18, "Family reunion refugees", 
                   19, "Polls federal election", 20, "AfD, Weidel in social media", 
                   21, "Women empowerment, M.Schwesig (SPD)", 22, "elections in Niedersachsen", 
                   23, "Court sentences, NSU trial", 24, "election capaigns & political talkshows", 
                   25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
                   28, "Turkey, Russia", 29, "railway problems (DBahn)", 30, "H.Kohl obituary", 
                   31, "AfD Gauland, Höcke", 32, "Asylum claims and deportation", 33, "EU policies", 
                   34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 37, "AfD in parliament", 
                   38, "Terror attacks (GER)  & police reports", 39, "Church", 40, "RAF"), ncol=2, byrow=T)

@@

top_topics <- theta %>% 
  group_by(document) %>%
  mutate(therank = rank(-gamma, ties.method = "random")) %>%
  filter(therank == 1) %>%
  select(- therank)

btw.2 <- btw %>%
  mutate(document = articleID) %>%
  inner_join(.,top_topics, by="document") %>%
  ## Combine with Topic label
  left_join(., topics.df, by="topic") %>%
  mutate(allocation = 1) 
```

### now we can inspect the unclear topics
```{r}
btw.2 %>% filter(topic==11) %>% select(title, gamma, url) %>%
  htmlTable::htmlTable(align="l")
```

@@

effect <- estimateEffect(c(1:40) ~ownership+s(month), stmOut, 
                         metadata = out_ownership$meta, uncertainty = "None")
#save(out_ownership,stmOut, effect, file = "stm_newsdata.RData")
```

@@

```{r}
p1 <- df %>%
  filter(corr>0.1 & corr < 1) %>%
  ggplot(aes(reorder(topic_name1,topic1), topic_name, 
             fill=corr)) +
  geom_tile() +
  facet_wrap(~site, ncol = 6) +
  #scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
  labs(x="", y="", fill="correlation") +
  theme_bw(base_family = "Roboto", base_size = 10) +
  theme(axis.text.x = element_text(angle=90, size = 6),
        #plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

@@

>>>>

# 2. Data 
```{r caching, echo = FALSE}
#load("../output/btw_combined.Rda")
load("../output/btw_comb.Rda")
```

@@

# 3. Model Results
```{r caching, echo = FALSE}
load("../output/models/STM_ownership 40 .Rda")
```

@@

After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
```{r}
sagelabs$cov.betas[[2]]$problabels[,1:5]
```

```{r}
topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition", 
                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder", 
                   7, "political trends after the election", 8, "Merkel vs.Schulz", 
                   9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
                   11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
                   12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg", 
                   15, "error (text processing failure)", 16, "Police academy (Berlin), AfD", 
                   17, "Federal budget statistics", 18, "Family reunion refugees", 
                   19, "Polls federal election", 20, "AfD in social media", 
                   21, "Women empowerment, M.Schwesig (SPD)", 22, "elections in Niedersachsen", 
                   23, "Court sentences, NSU trial", 24, "election campaigns & political talkshows", 
                   25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
                   28, "Turkey, Russia", 29, "A.Merkel in east GER", 30, "H.Kohl obituary", 
                   31, "AfD (Petri, Gauland, Höcke)", 32, "Asylum claims and deportation", 
                   33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
                   37, "AfD in parliament", 38, "Church", 39, "Terror attacks (GER)  & police reports", 
                   40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)

@@

top_topics <- theta %>% 
  group_by(document) %>%
  mutate(therank = rank(-gamma)) %>%
  filter(therank == 1) %>%
  select(- therank)

btw.2 <- btw %>%
  mutate(document = articleID) %>%
  merge(.,top_topics, by="document") %>%
  ## Combine with Topic label
  merge(., topics.df, by="topic") %>%
  mutate(allocation = 1) 
```

### now we can inspect the unclear topics
```{r}
btw.2 %>% filter(topic==17) %>% select(title, gamma, site) %>%
  arrange(desc(gamma)) %>%
  htmlTable::htmlTable(align="l")
```

@@

effect <- estimateEffect(c(1:40) ~ownership+s(month), stmOut, 
                         metadata = out$meta, uncertainty = "None")
#save(out_ownership,stmOut, effect, file = "stm_newsdata.RData")
```

@@

```{r}
p1 <- df %>%
  filter(corr>0.05 & corr < 1) %>%
  ggplot(aes(reorder(topic_name1,topic1), topic_name, 
             fill=corr)) +
  geom_tile() +
  facet_wrap(~site, ncol = 6) +
  #scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
  labs(x="", y="", fill="correlation") +
  theme_bw(base_family = "Roboto", base_size = 10) +
  theme(axis.text.x = element_text(angle=90, size = 6),
        #plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

@@

Take a closer look to those topics that are discussed most different.

```{r}
plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[29,], collapse="\n"),
            paste(sagelabs$cov.betas[[2]]$problabels[29,], collapse="\n")))
```

```{r}
btw.2 %>%
  filter(grepl("sturm", url) &
           site == "Tagesschau.de") %>%
  select(title, site)
```
